---
title: "Reactive, Isolate and Observe"
author: "Divya Sherwani"
date: "July 14, 2021"
output: word_document
---

```{r}
library(shiny)
```

## Render function example

There are two inputs (number and text) and one output (histrogram with title).

```{r}
ui <- fluidPage(
  sliderInput(inputId='num',
              label='Choose a number',
              value=25,min=1,max=100),
  textInput(inputId = 'title',
            label='Write a title',
            value = 'Histogram of random values'),
  plotOutput("hist")
)

server <- function(input, output, session) {
  output$hist<-renderPlot({
    hist(rnorm(input$num),main=input$title)
  })
  
}
```

## Reactive Value code

There is one input (value) and one output (histogram).

```{r}
ui <- fluidPage(
  sliderInput(inputId='num',
              label='Choose a number',
              value=25,min=1,max=100),
  plotOutput("hist")
)

server <- function(input, output, session) {
  output$hist<-renderPlot({hist(rnorm(input$num))})
  
}
```


## Single reactive value to update 2 functions

There is one input (number) and two outputs (histrogram and summary statistics).

```{r}
ui <- fluidPage(
  sliderInput(inputId='num',
              label='Choose a number',
              value=25,min=1,max=100),
  plotOutput("hist"),
  verbatimTextOutput("stats")
)

server <- function(input, output) {
  output$hist<-renderPlot({
    hist(rnorm(input$num))
  })
  output$stats<-renderPrint({
    summary(rnorm(input$num))
  })
  
}
```

## Reactive expression

When there is one input and multiple outputs, instead of specifying the input every time, we can specify the input in the reactive function.

```{r}
ui <- fluidPage(
  sliderInput(inputId='num',
              label='Choose a number',
              value=25,min=1,max=100),
  plotOutput("hist"),
  verbatimTextOutput("stats")
)

server <- function(input, output) {
  data<-reactive({rnorm(input$num)})
  output$hist<-renderPlot({hist(data())})
  output$stats<-renderPrint({summary(data())})
  
}
```

## Isolate function

```{r}
ui <- fluidPage(
  sliderInput(inputId='num',
              label='Choose a number',
              value=25,min=1,max=100),
  textInput(inputId = 'title',
            label='Write a title',
            value = 'Histogram of random values'),
  plotOutput("hist")
)

server <- function(input, output, session) {
  output$hist<-renderPlot({
    hist(rnorm(input$num),main=isolate(input$title))
  })
  
}
```


## Action button : Observe function

In order to perform any operation and not show the user, the observe evenet function can be used.

```{r}
ui <- fluidPage(
  actionButton(inputId = "clicks",
               label = "Click Me")
)

server <- function(input, output, session) {
  observeEvent(input$clicks,{print(as.numeric(input$clicks))})
  
}

```


